### 2020-10-07 thesis/msc-thesis.tex
add bullet points

     \item Solution for CSS Problems
     \begin{enumerate}
          \item One CSS providing company, which integrates multiple / all EA
          \item One identity, profile, address, phone number location
          \item Easy management of identity used by multiple enterprises / organizations
     \end{enumerate}

@@

\begin{enumerate}
     \item What are challenges of integration?
     \begin{enumerate}
          \item Heterogeneous Enterprise Architecture Systems
          \begin{enumerate}
               \item Different Applications
               \item Different Application Vendors
               \item Different Application Interfaces
               \item No Application Interfaces
               \item Legacy Systems
          \end{enumerate}

          \item Different (proprietary) data models within and between Enterprises and Organizations

          \item Stability of Integration
          \begin{enumerate}
               \item Future Changes of EA
               \item Scalability
               \item Failure of EA or Integration Components
               \item ...
          \end{enumerate}

@@

          \item Integration Patterns
          \begin{enumerate}
               \item Patterns speed up construction of Integration Architecture
               \item Patterns are proven solutions
               \item Patterns abstract from possible technologies
               \begin{enumerate}
                    \item Simplifies understanding of integration concept
                    \item Allows implementation with different technologies
               \end{enumerate}

@@

\section{Customer Self-Service}

\begin{enumerate}
     \item Definition of CSS
     \item What is CSS and why is it important?
     \item How to document CSS-Scenarios
     \item List of important CSS-Scenarios
     \begin{enumerate}
          \item Criteria for importance
     \end{enumerate}
\end{enumerate}

\section{Architecture Patterns}

\begin{enumerate}
     \item Definition
     \item Patterns relevant for CSS
     \item Relevant Architecture bricks and data bricks
\end{enumerate}

\section{Business Connector}

\section{Integration Patterns}

@@

\section{Overview and objective}
\label{sec:overview}

\section{First part}
\label{sec:teil1}

\section{Second part}
\label{sec:teil2}

Usw.

>>>>

     \item Solution for CSS Problems
     \begin{enumerate}
          \item One CSS providing company, which integrates multiple / all EA
          \item One identity, profile, address, phone number, location, ...
          \item Easy management of identity used by multiple enterprises / organizations
     \end{enumerate}

@@

\begin{enumerate}
     \item What are challenges of integration?
     \begin{enumerate}
          \item Heterogeneous Enterprise Architecture Systems
          \begin{enumerate}
               \item Different Applications
               \item Different Application Vendors
               \item Different / No Application Interfaces
               \item Legacy Systems
          \end{enumerate}

          \item Different (proprietary) data models within and between Enterprises and Organizations
          \begin{enumerate}
               \item Different (property)name for same data objects (syntactic integration)
               \item Different meanings for same (property)name (semantic integration)
          \end{enumerate}

          \item Stability of Integration
          \begin{enumerate}
               \item Future Changes of EA
               \item Scalability
               \item Failure of EA or Integration Components
          \end{enumerate}

@@

          \item Integration Patterns
          \begin{enumerate}
               \item Patterns speed up construction of Integration Architecture
               \item Patterns are proven solutions
               \item Patterns abstract from concrete technologies
               \begin{enumerate}
                    \item Simplifies understanding of integration concept
                    \item Allows implementation with different technologies
               \end{enumerate}

@@

\section{Customer Self-Service}
\begin{enumerate}
     \item What is CSS
     \begin{enumerate}
          \item Definition in the context of the thesis
     \end{enumerate}

     \item How to document CSS-Scenarios
     \item List of CSS-Scenarios
     \item Purpose of CSS-Scenarios in the thesis
     \begin{enumerate}
          \item Finding relevant EAPs
          \item Requirement analysis of business Connector
          \item Interface definition of business connector
     \end{enumerate}

\section{Architecture Patterns}
\begin{enumerate}
     \item What is an EAP
     \begin{enumerate}
          \item Definition
          \item Metadata
          \item Views
          \item Architecture bricks
          \item Data bricks
          \item Business processes
     \end{enumerate}

     \item Purpose of an EAP in this context
     \begin{enumerate}
          \item Basis for real-life enterprise architectures
          \item Provides architecture and data bricks the integration can build up on
     \end{enumerate}

     \item Short description of EAPs in the book
     \item Patterns relevant for CSS
     \begin{enumerate}
          \item Derived by comparing CSS-Scenarios with business processes
     \end{enumerate}

     \item Relevant Architecture bricks and data bricks for CSS-Scenarios
     \item How to document relevant bricks for usage of the integration Architecture
     \item Documentation of relevant bricks
     \item List of requirements regarding the integration Architecture
     \item \begin{enumerate}
          \item Adapters for systems
          \item Required Format of incoming data
     \end{enumerate}

\section{Business Connector}
\begin{enumerate}
     \item What is a business connector?
     \begin{enumerate}
          \item Provides functionality of "external" service provider
          \item Purpose is to simplify integration
          \item Can be assumed to provide sufficient interfaces
     \end{enumerate}

     \item Purpose of business connector in context of the thesis
     \begin{enumerate}
          \item Provides interface for CSS functionalities
          \item Should be integrated in architecture and data bricks
     \end{enumerate}

     \item How to document the business Connector in this context
     \begin{enumerate}
          \item List of provided functionalities along with their interfaces
          \begin{enumerate}
               \item Derived from CSS-Scenarios
               \item Derived from IDAS Connector
          \end{enumerate}

          \item List of requirements regarding the EA
          \begin{enumerate}
               \item Access to architecture and data bricks
          \end{enumerate}

          \item List of requirements regarding the integration Architecture
          \begin{enumerate}
               \item Format of data
               \item Order of delivery
               \item Time relevance of data
               \item Guaranteed delivery of data
          \end{enumerate}

\section{Integration Patterns}
\begin{enumerate}
     \item What are Integration Patterns?
     \begin{enumerate}
          \item Messaging Methodology
          \item Patterns describe often solved messaging problems
     \end{enumerate}

     \item What is their purpose in this context
     \begin{enumerate}
          \item Already explained in Motivation?
     \end{enumerate}

     \item Description of Patterns later used in the integration architecture
\end{enumerate}

@@

\section{Overview}
\label{sec:overview}
